\chapter{Introduction}
\todo[inline]{Lada:bold font: formulace, ktere by se IMHO daly vylepsit, red color: zavacejici nebo vyrazne nevhodne formulace - je treba vylepsit, -- : text bych doporucil vymazat. Snad jsem ti nerozesral build, nemam tady ve vlaku moc moznost to zkompilovat}
Millions of songs online provide an opportunity to find great songs for people with all kinds of music tastes. However, only a small fraction of {\bf the magnitude of all the songs} produced becomes popular. Those are the ones people are being exposed to the most. {\bf They are recommended to them} on various platforms such as YouTube \footnote{https://www.youtube.com} or Spotify \footnote{https://www.spotify.com}, and played across all radio stations sometimes several times a day. After a while, older songs become less popular, one could use the term \textit{"overplayed"} and other (usually new) songs take their place. But what if a person's next favorite song already existed, it just did not become popular? It is unlikely to hear unpopular but possibly likeable songs for people with unusual music preferences on the radio. Radio stations try to target as many listeners as possible. However, with the assistance of a recommender collecting data about what a user listens to, it could help anyone discover tracks perfectly tailored for them without being dependant on their popularity.\\
The suggestions of recommendation systems for basically any online content are crucial. With the amount of songs {\bf but also} movies, books, clothes, electronics and many more, it would be extremely time consuming for a person to go through all of {\bf it (them/the objects)} in order to find what they are looking for. Recommendation systems are trying to make it easier for people to find what they want and even predict, what they will be looking for next or what they might want but maybe just do not know it yet.\todo{trochu slozita, kostrbata veta} \\
There are three main method groups to generate (not only) music recommendations for users. First are collaborative-filtering methods (CF) where recommendations are based on like-minded users preferences \todo{the preferences of like-minded users}, second are content-based methods where recommendations are based on the song content (tags, audio, lyrics, ...) and the third group are hybrid methods combining the first two together. \\
Generally, CF methods for all kinds of recommendation systems appear to be researched more extensively \cite{DBLP:journals/corr/abs-1712-07525} however, there are certain drawbacks {\bf (of) these approaches}. Most obviously, there is a problem with new, unrated songs because no user has viewed or liked them, so they cannot be recommended to like-minded users with a method based only on collaborative filtering. This is called the cold-start problem. Also, the recommendations tend to be dependent on user popularity patterns. Nevertheless, with enough user data, collaborative filtering methods generally outperform content-based methods \cite{van2013deep}. \\
Due to {\bf this (observation)}, there are not many applications that would recommend songs based solely on their content and to the best of our knowledge, there is no music recommendation application that would recommend songs to its users based only on lyrics. As this is a logical consequence of the findings above, we believe that a recommendation system based exclusively on content-based methods could be helpful for users with an unusual taste because collaborative filtering is popularity-dependant. Therefore the goal of this thesis to introduce such {\bf an} application. \\
{\bf(In order)} To create a content-based music recommender application we need to decide {\bf based on what content it will be recommending (the source(s) of content information)}. A basic CB recommendation {\bf -- of songs -- } is attribute-based. {\bf (Common)} Attributes {\bf (of songs)} are {\bf --the song's--}  genre, the artist, creation year and so on. {\bf We are not using it in our application however (Nonetheless, we decided not to use these simple CB attributes in this thesis,)} because almost all music related application allow users to search based on tags so it would not bring anything new really. \\
{\bf (Instead of simple CB attributes,)}We chose lyrics and audio as the {\bf (sources of)} content{\bf information. -- songs have to base the recommendations of the application on--}. {\bf Audio is something that every song has and it also is probably what is most important about it.} \todo{Audio channel of the song is probably the ultimate low-level content information of every song.} People listen to music because it is a pleasant sound and it is likely that it is audio features that define, whether a person likes a song or not. \todo{Co neco jako: On the other hand, processing song's audio channel to some meaningful features is an expensive and complex task with many options and hyperparameters that need to be set.}\\
\todo{Co neco jako: Song lyrics, i.e., a textual transcript of the speech given in the song is a somewhat less informative, however it may still possess valuable information, for which, more processing methods were already developed and the process of transforming raw lyrics into some meaningful attributes is less demanding compared to the processing of raw audio.} {\bf With lyrics it is a bit different. The main reason to study these methods is the lack of research for lyrics-based methods.} There is an intuitive a notion that their performance might be doubtful, however, many studies evaluate them on their genre classification accuracy \cite{DBLP:journals/corr/Tsaptsinos17} or compare them to collaborative filtering systems \cite{Gossi2016LyricBasedMR} which does not always mimic actual user behaviour. \\
Recommendation is mostly based on similarity between items which can be defined in various ways. Both lyrics and audio need pre-processing before establishing similarity. \todo{mozna zminit ze je rada moznosti jak to udelat} Because of that the goal of this thesis is to describe and test various ways of pre-processing text and audio signals in an unsupervised manner for content-based song similarity calculations, select some of them based on previous studies and features, evaluate their performance on real user playlists, compare their performance and then implement chosen ones in a web application.\todo{dlouha veta, rozdelit}\\
During our research it turned out that measuring song similarity based on lyrics and based on audio are two completely different tasks and there are multiple sub-problems in both approaches. \todo{Although it originally seemed that processing both content modalities are similar, during our work on the thesis, it turned out that the complexity and diversity of the pre-processing steps exceeded our expectations.} Language, feature representation and similarity metrics for lyrics based methods and audio extraction, audio representation, feature extraction and similarity metrics for audio based similarity. {\bf (Therefore,)} We decided to focus on unsupervised learning of song feature representation which means encoding a song into a vector so that a standard similarity-based recommendation technique can be used to evaluate similarity of two arbitrary songs without having any information about genre or other tags.\todo{dlouha veta, rozdelit} The vectors can also be used for more advanced algorithms using for example Recurrent neural networks to calculate similarity. That is however above the scope of this work. \\
The methods will be divided into two main groups. In the first one, songs will be encoded based on their lyrics in the second one based on audio. In both groups, we described basic as well as more advanced existing unsupervised learning encoding methods. We compare the text and audio recommendations based on these encoding methods but also compare methods within these two groups. \\
The web applications main purpose is to introduce the user to new songs he has not listened to yet based on a feature extraction method he chooses. The songs are provided by the applications default database but adding songs is possible too and their distance to other songs is taken into account for recommendations. \\


